Optimal Fitting of Planar Curves to Prescribed Constraints

### 2014-02-01 idp/documents/documentation/paper.tex
more restructuring

\input{../common/math.tex}     % some math helper macros

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{../content/common/examples_bezier.pdf}
					\caption{Bézier Spline Examples (left: Fluttershy \cite{fluttershy}, right: Lugia \cite{lugia})}
					\label{figure:examples_bézier}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{../content/common/examples_spiro.pdf}
					\caption{Spiro Spline Examples (left: Fluttershy \cite{fluttershy}, right: Lugia \cite{lugia})}
					\label{figure:examples_spiro}
				\end{figure}

@@

			\begin{figure}[htbp]
				\centering
				\includegraphics[width=\textwidth]{../content/common/description-based_curves.pdf}
				\caption{Description-Based Curves}
				\label{figure:description-based_curves}
			\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{../content/documentation/fairness_mec.pdf}
					\caption{Minimum Energy Curves}
					\label{figure:minimum_energy_curves}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{../content/documentation/fairness_mvc.pdf}
					\caption{Minimum Variation Curves}
					\label{figure:minimum_variation_curves}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=100mm]{../content/common/linear_segmentation.pdf}
					\caption{Linear Segmentation}
					\label{figure:linear_segmentation}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{../content/documentation/subsystems.pdf}
					\caption{Subsystem Decomposition of the Kurve Project}
					\label{figure:subsystem_decomposition}
				\end{figure}

@@

			\subsection{Specification}
				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{../content/documentation/specification_class_diagram.pdf}
					\caption{Class Diagram of Specification-Related Classes}
					\label{figure:specification_class_diagram}
				\end{figure}

@@

			\subsection{Optimization}
				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{../content/documentation/optimization_class_diagram.pdf}
					\caption{Class Diagram of Optimization-Related Classes}
					\label{figure:optimization_class_diagram}
				\end{figure}

@@

		\section{User Interface}
			\subsection{Implementation}
				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{../content/documentation/ui_components_class_diagram.pdf}
					\caption{Class Diagram of the User Interface Components}
					\label{figure:ui_components_class_diagram}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{../content/documentation/ui_components.pdf}
					\caption{Overview of the User Interface in Kurve}
					\label{figure:ui_components}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{../content/documentation/ui_speeds.pdf}
					\caption{Example of a Curve that is `Overspecified' (i.e. the speed of the curve cannot be kept constant due to the high amount of constraints)}
					\label{figure:ui_speeds}
				\end{figure}

@@

			\begin{figure}[htbp]
				\centering
				\includegraphics[width=\textwidth]{../content/common/examples_prototype.pdf}
				\caption{Prototype Curve Design Tool Examples (left: Fluttershy \cite{fluttershy})}
				\label{figure:examples_prototype}
			\end{figure}

>>>>

\input{math.tex}               % some math helper macros

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/examples_bezier.pdf}
					\caption{Bézier Spline Examples (left: Fluttershy \cite{fluttershy}, right: Lugia \cite{lugia})}
					\label{figure:examples_bézier}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/examples_spiro.pdf}
					\caption{Spiro Spline Examples (left: Fluttershy \cite{fluttershy}, right: Lugia \cite{lugia})}
					\label{figure:examples_spiro}
				\end{figure}

@@

			\begin{figure}[htbp]
				\centering
				\includegraphics[width=\textwidth]{content/output/description-based_curves.pdf}
				\caption{Description-Based Curves}
				\label{figure:description-based_curves}
			\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/fairness_mec.pdf}
					\caption{Minimum Energy Curves}
					\label{figure:minimum_energy_curves}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/fairness_mvc.pdf}
					\caption{Minimum Variation Curves}
					\label{figure:minimum_variation_curves}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=100mm]{content/output/linear_segmentation.pdf}
					\caption{Linear Segmentation}
					\label{figure:linear_segmentation}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/subsystems.pdf}
					\caption{Subsystem Decomposition of the Kurve Project}
					\label{figure:subsystem_decomposition}
				\end{figure}

@@

			\subsection{Specification}
				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/specification_class_diagram.pdf}
					\caption{Class Diagram of Specification-Related Classes}
					\label{figure:specification_class_diagram}
				\end{figure}

@@

			\subsection{Optimization}
				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/optimization_class_diagram.pdf}
					\caption{Class Diagram of Optimization-Related Classes}
					\label{figure:optimization_class_diagram}
				\end{figure}

@@

		\section{User Interface}
			\subsection{Implementation}
				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/ui_components_class_diagram.pdf}
					\caption{Class Diagram of the User Interface Components}
					\label{figure:ui_components_class_diagram}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/ui_components.pdf}
					\caption{Overview of the User Interface in Kurve}
					\label{figure:ui_components}
				\end{figure}

@@

				\begin{figure}[htbp]
					\centering
					\includegraphics[width=\textwidth]{content/output/ui_speeds.pdf}
					\caption{Example of a Curve that is `Overspecified' (i.e. the speed of the curve cannot be kept constant due to the high amount of constraints)}
					\label{figure:ui_speeds}
				\end{figure}

@@

			\begin{figure}[htbp]
				\centering
				\includegraphics[width=\textwidth]{content/output/examples_prototype.pdf}
				\caption{Prototype Curve Design Tool Examples (left: Fluttershy \cite{fluttershy})}
				\label{figure:examples_prototype}
			\end{figure}
